Proportional multi-state multiple-cohort life table model

### 2018-04-10 MSLT/MSLTdoc.Rmd
Change plot type for mortality rates comparison

##Plot all cause mortality rates males 
mx_plot_compare_male <- ggplot() + 
geom_line(data=ggplot_data_England, aes(x= age_cat, y= one_rate), color='green') +
geom_line(data=ggplot_data_GL, aes(x= age_cat, y= one_rate), color='red') +
xlab ("Age") + ylab ("Rate per one") + labs (title = "Mortality rates comparison") +
theme_classic() +
scale_alpha_manual("Location", values = c("England", "Greater London")) +

#Print to view
print(mx_plot_compare_male)

>>>>

##Plot all cause mortality rates males 
mx_plot_compare_male <- ggplot(ggplot_data_England, aes(age_cat,one_rate))+
    geom_line(aes(color = "England"))+
    geom_line(data=ggplot_data_GL,aes(color="Greater London"))+
    labs(colour="Locations",x="Age",y="Mortality rate")+
    theme(legend.position = c(0, 1),legend.justification = c(0, 1))+
    scale_color_manual(values = c("blue","red"))+
    theme_classic()

print(mx_plot_compare_male)
